Questions to Developers

### 2021-06-25 StateOfPractice/Ao-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
updated painpoints

\structure{Do these fit with your experience?}
\bi
\item Lack of time to implement new features
\item Team members lack software development experience
\item Lack of funding for software development
\item No organizations to help with developing high quality software
\item Difficulty to get test data
  \ei

>>>>

\structure{Do these fit with your experience?}
\bi
\item Lack of time to 1) implement all requested new features 2) write and maintain good documents 3) review all contributions from the community
\item It is difficult to find or keep the members with experience in both software development and medical imaging
\item Lack of funding for software development (especially for maintenance)
\item No organizations to help with developing high quality software
\item Difficulty to get test data
\item Difficulty to achieve cross-platform compatibility: 1) native app - more time and work 2) web app w/o server - worse performance 3) web app w/ servers - more cost
\ei
